---
title: "Donor obfuscation"
author: "SG"
date: "25 November 2018"
output:
  md_document:
    variant: markdown_github
  html_document: default
---

# Rationale

To preserve confidentiality while allowing public collaboration, we require obfuscated donor and service data for model-building. The obfuscated data should have similar distributional (geospatial and demographic) properties to the real data.

# Method

* Data are resonably anonymised already.
* Apply a random offset (up to +/- 6 months) to date variables.
* Don't set a RNG seed.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = FALSE)
```

```{r}
library(lubridate)
library(readxl)
library(here)
library(tidyverse)
```

Simple string normalisation:

```{r}
str_normalise <- function(str){
  str %>%
    toupper %>%
    str_remove_all("\\W")
}
```

Import and clean real dataset (not pushed to Github):

```{r import/donors}
donors_raw <- read_csv(here("data/raw/donors.csv"), col_types = "ccccccc")

donors <- donors_raw %>%
  mutate(gender = factor(gender),
         
         state = str_normalise(state) %>% 
           fct_collapse(ACT = c("ACT", "AUSTRALIANCAPITALTERRITORY"),
                        NSW = c("NSW", "NEWSOUTHWALES"),
                        QLD = c("QLD", "QUEENSLAND"),
                        SA = c("SA", "SOUTHAUSTRALIA"),
                        TAS = c("TAS", "TASMANIA"),
                        VIC = c("VIC", "VICTORIA"),
                        WA = c("WA", "WESTERNAUSTRALIA")) %>%
           fct_other(keep = c("ACT", "NSW", "QLD", "SA", "TAS", "VIC", "WA"),
                     other_level = NA_character_),
         
         postcode = case_when(state == "NT" & str_detect(postcode, "^8[0-9]{2}$") ~
                                paste0("0", postcode),
                              str_detect(postcode, "^[0-9]{4}$") ~ postcode,
                              TRUE ~ NA_character_) %>%
           factor) %>%
  mutate_at(vars(dateofbirth, FirstContributionDate, LastContributionDate),
            function(v) {
              str_remove(v, " .*$") %>%
                ymd %>%
                na_if(ymd("1900-01-01")) %>%
                if_else(. > ymd("2018-11-24"), as.Date(NA), .)
            })

summary(donors)
```

Obfuscate with date offset:

```{r donors/obfuscate}
n <- nrow(donors)
range <- 365
offset_days <- runif(n, min =  -range / 2, max = range / 2)

donors_obf <- donors %>%
  mutate_at(vars(dateofbirth, FirstContributionDate, LastContributionDate), 
            ~ . + offset_days)

summary(donors_obf)
```

Write out for future use:

```{r donors/write}
saveRDS(donors_obf, here("data/clean/donors_obf.rds"))
write_csv(donors_obf, here("data/clean/donors_obf.csv"))
```
