---
title: "POA-level model"
author: "SG"
date: "06/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(sf)
library(pxR)
library(tidyverse)
library(here)
library(readxl)
```

# Datasets

The census data used below (`seifa_poa`, filename [data/raw/seifa2016_poa.px](../data/raw/seifa2016_poa.px)) are the [2016 Socio-economic indices for Australia](http://stat.data.abs.gov.au/Index.aspx?DataSetCode=SEIFA_POA) for postal area statistical areas, provided by the [Australian Bureau of Statistics](http://stat.data.abs.gov.au/Index.aspx) under the [CC BY 2.5 AU](https://creativecommons.org/licenses/by/2.5/au/) license. 

Import and tidy (obfuscated donor data, service data, census data):

```{r data}
donors_poa <- readRDS(here("data/clean/donors_obf.rds")) %>%
  select(poa = postcode) %>%
  group_by(poa) %>%
  summarise(donors = n())

seifa_poa <- read.px(here("data/raw/seifa2016_poa.px")) %>%
  as.tibble %>%
  na.omit %>%
  mutate(index_measure = paste(Index.Type, Measure, sep = " - ")) %>%
  select(poa = Postal.Area.Code, index_measure, value) %>%
  spread(key = index_measure, value = value) %>%
  rename(pop = `Index of Relative Socio-economic Disadvantage - Usual resident population`) %>%
  select(-contains("Usual resident population")) %>%
  mutate(poa = if_else(str_detect(poa, "^8"),
                      paste0("0", poa),
                      as.character(poa)))

services_poa <- read_excel(here("data/raw/Service Details.xlsx")) %>%
  select(`Post Code`) %>%
  transmute(poa = factor(`Post Code`)) %>%
  group_by(poa) %>%
  summarise(services = n())
```

Spatial boundaries for each POA are also provided by the ABS:

```{r spatia}
target <- tempfile()
unzip(here("data/raw/1270055003_poa_2016_aust_shape.zip"),
      exdir = target)

poa_spatial <- st_read(paste(target, "POA_2016_AUST.shp", sep = "/"))
```

Merge and compute normalised donor and service densities:

```{r joins}
poas <- seifa_poa %>%
  left_join(donors_poa, by = "poa") %>%
  left_join(services_poa, by = "poa") %>%
  left_join(select(as.data.frame(poa_spatial), poa = POA_CODE16, area = AREASQKM16)) %>%
  mutate_at(c("donors", "services"), ~coalesce(.x, 0L)) %>%
  mutate(pop_density = pop / area,
         donors_norm = donors / pop * 1e5,
         services_norm = services / pop * 1e5)
```


Still to do:

* Actual modelling!
